Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-06 longSC.tex
alice's comment English first part

The main emphasis of the ultra-relativistic heavy-ion collisions at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study deconfined phase of the strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP). 
This matter exhibits strong collective and anisotropic flow in the plane transverse to the beam direction, which is driven by the anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} continues to increase also at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}. This has been predicted by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
%and microscopic transport models ~\cite{Xu:2007jv}.  
These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of QGP is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de} in heavy-ion collisions at RHIC and LHC energies.

The temperature dependence of the $\eta/s$ has some generic features that most of the known fluids obey. For instance, one such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}. 
It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy ratio value found in nature. Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be calculated using the AdS/CFT correspondence~\cite{Kovtun:2004de}. Hydrodynamical simulations support as well the view that $\eta/s$ of the QGP matter is close to that limit~\cite{Gale:2012rq}. This may have important implications for other fundamental physics goals. It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc,Csernai:2006zz}.
%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.

%The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in the Fourier decomposition of particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:

@@

\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic. $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
%Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
%\begin{equation}
%\label{defVn}
%P(\varphi)=\frac{1}{2\pi}\sum_{n=-\infty}^{+\infty}V_n e^{-in\varphi},
%\end{equation}
%where $V_n$ is the (complex) anisotropic flow coefficient in the $n$th harmonic.
%One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
The anisotropic flow in heavy-ion collisions is understood as hydrodynamic response of produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
This profile fluctuates event-by-event due to fluctuating position of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
The recognition of the importance of flow fluctuations led to triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlation between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
%The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
The higher order harmonics are expected to be sensitive to fluctuations in the initial conditions and to the magnitude of $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while $v_{n}$ correlations have the potential to discriminate between these two respective contributions~\cite{Niemi:2012aj}.
%And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.

Difficulties in extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
The viscous effects reduce the magnitude of the elliptic flow. Furthermore, the magnitude of $\eta/s$ used in hydrodynamic calculations should be considered as an average over the temperature evolution of the expanding fireball as it is known that $\eta/s$ of other fluids depends on temperature. 
In addition, part of the elliptic flow can also originate from the hadronic phase~\cite{Bozek:2011ua,Rose:2014fba,Ryu:2015vwa}. Therefore,
knowledge of both the temperature dependence of $\eta/s$ and the relative contributions from the partonic and hadronic phases should be understood better to quantify $\eta/s$ of the partonic fluid.

An important input to the hydrodynamic model simulations is the distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricity~\cite{Alver:2010gr},
\begin{equation}
 \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
  \label{eq:eccentricities}
\end{equation}
where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g. $v_n \propto \varepsilon_n$ for n=2 or 3).
$v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
The higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}. When the order of harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and become larger for more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
Hence the studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.

Recently, ALICE Collaboration measured for the first time the new multiparticle observables, the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}. 
The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
In this article, we have extended the analysis of SC observables to higher order Fourier harmonics (up to $5^{\mathrm{th}}$ order) as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also include extensive comparison to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods. The experimental setting and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. The results of the measurements are presented in Sec.~\ref{sec:results}. 
 In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations. Various theoretical models used in the article are described in Sec.~\ref{sec:theory}. Sec.~\ref{sec:summary} summarizes our findings.

@@

The existing measurements provide an estimate of the average value of QGP's $\eta/s$, both at RHIC and LHC energies. What remains uncertain is how the $\eta/s$ of QGP depends on temperature ($T$). The temperature dependence of $\eta/s$ in the QGP was discussed in ~\cite{Csernai:2006zz}. The effects to hadron spectra and elliptic flow were studied in ~\cite{Niemi:2011ix} for different parametrizations of $\eta/s(T)$.  A more systematic study with the event-by-event EKRT+viscous hydrodynamic calculations has been just initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein). The emerging picture is that the study of individual flow harmonics $v_n$ will unlikely reveal the details of $\eta/s(T)$ dependence.
It was demonstrated already in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics. In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$. These new observables have potential to discriminate the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}. Therefore their measurements would provide the experimental constrains of the theoretical predictions for individual stages of heavy-ion evolution independently. In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.

For reasons discussed in \cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced in \cite{Niemi:2012aj}. 
Based on \cite{Bilandzic:2013kga}, the new flow observables obtained from multiparticle correlations, so-called \textit{Symmetric Cumulants~(SC)}, were introduced. SC observables are nearly insensitive to nonflow and quantify the correlation of amplitudes of two different flow harmonics.
The first measurements of SC observables were recently published by ALICE Collaboration in \cite{ALICE:2016kpq}.

The SC observables are defined as (for details see Sec.~IV~C in~\cite{Bilandzic:2013kga}):
 %
%\begin{widetext}
\begin{eqnarray}
\left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
&&{}-\left<\left<\cos[m(\varphi_1\!-\!\varphi_2)]\right>\right>\left<\left<\cos[n(\varphi_1\!-\!\varphi_2)]\right>\right>\nonumber\\
&=&\left<v_{m}^2v_{n}^2\right>-\left<v_{m}^2\right>\left<v_{n}^2\right>\,,%\nonumber\\
%&=&0\,.
\label{eq:4p_cumulant}
\end{eqnarray}
%\end{widetext}
%
with the condition $m\neq n$ for two positive integers $m$ and $n$.
In this article SC($m$,$n$) normalized with the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$~\cite{ALICE:2016kpq,Giacalone:2016afq}, is denoted by NSC($m$,$n$):
%
\begin{equation}
\mathrm{NSC}(m,n) \equiv \frac{\mathrm{SC}(m,n)}{\left<v_{m}^2\right>\left<v_{n}^2\right>}\,.
\label{eq:nsc}
\end{equation}
%
Normalized symmetric cumulants reflect only the degree of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ contains both the degree of the correlations between two different flow harmonics and individual $v_{n}$ harmonics. In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations using a pseudorapidity gap of $|\Delta\eta|>1.0$ which suppresses biases from few-particle nonflow correlations. For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}) the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this case. This was verified by HIJING model simulations in \cite{ALICE:2016kpq}.

The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}. However, the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}. The observed centrality dependence of SC(4,2) cannot be captured with the constant $\eta/s$ dependence, indicating clearly that the temperature dependence plays an important role. These results were also used to discriminate between different parameterizations of initial conditions. It was demonstrated that in the fluctuation-dominated regime (central collisions) MC-Glauber initial conditions with binary collisions weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.

\section{Data Analysis}
\label{sec:experiment}
A sample of $\PbPb$ collisions at $\snn=2.76$~TeV recorded by ALICE during the 2010 heavy-ion run at the
LHC is used for this analysis. Detailed descriptions of the ALICE
detector can be found
in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
Projection Chamber (TPC) was used to reconstruct charged particle
tracks and measure their momenta with full azimuthal coverage in the
pseudorapidity range $|\eta|<0.8$. Two scintillator
arrays (V0) which cover the pseudo-rapidity ranges $-3.7<\eta<-1.7$
and $2.8<\eta<5.1$ were used for triggering and the determination of
centrality~\cite{Aamodt:2010cz}. The trigger
conditions and the event selection criteria are identical to those
described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
Approximately $10^7$ minimum-bias $\PbPb$ events with
a reconstructed primary vertex within $\pm 10$ cm from the nominal
interaction point in the beam direction are selected. Charged particles reconstructed in the TPC in $|\eta|<0.8$
and $0.2<p_{\rm T}<5$~GeV/$c$ were selected. The charged track quality cuts
described in~\cite{Aamodt:2010pa} were applied to minimize
contamination from secondary charged particles and fake tracks.
The reconstruction efficiency and contamination of charged particles
were estimated from HIJING Monte Carlo
simulations~\cite{Wang:1991hta} combined with a GEANT3~\cite{Brun:1994aa} detector model and were found to be independent of
the collision centrality. The reconstruction efficiency increases from
70\% to 80\% for particles with $0.2<p_{\rm T}<1$~GeV/$c$ and remains
constant at $(80 \pm 5)$\% for $p_{\rm T}>1$~GeV/$c$. The estimated
contamination by secondary charged particles from weak decays and
photon conversions is less than 6\% at $p_{\rm T}=0.2$~GeV/$c$ and falls
below 1\% for $p_{\rm T}>1$~GeV/$c$.
The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the contribution to the anisotropies from jets. 
Reconstructed TPC tracks were required to have at least 70 space points (out of a maximum of 159). 
Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in longitudinal and transverse direction, are accepted. This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc. Tracks with kinks (the tracks that appear to change direction due to multiple scattering, $K^{\pm}$ decays) were rejected.

@@

The systematic uncertainties are estimated by varying the event and track selection criteria. All systematic checks described here are performed independently. 
All results of SC$(m,n)$ with a selected criterion are compared to ones from the default event and track selection described in the previous section.
The differences between the default results and the ones obtained from the variation of the selection criteria are taken as systematic uncertainty of each individual source.
The contributions from different sources were added in quadrature to obtain the total systematic uncertainty.

>>>>

The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP). 
This matter exhibits strong collective and anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} is also observed at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}. This has been predicted by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
%and microscopic transport models ~\cite{Xu:2007jv}.  
These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of the QGP in heavy-ion collisions at RHIC and LHC energies is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de}.

The temperature dependence of $\eta/s$ has some generic features that most known fluids obey. For instance, one such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}. 
It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature. Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be calculated using AdS/CFT correspondence~\cite{Kovtun:2004de}. Hydrodynamical simulations also support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}. This may have important implications for other fundamental physics goals. It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental study~\cite{Lacey:2006bc,Csernai:2006zz}.
%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.

%The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:

@@

\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic. $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
%Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
%\begin{equation}
%\label{defVn}
%P(\varphi)=\frac{1}{2\pi}\sum_{n=-\infty}^{+\infty}V_n e^{-in\varphi},
%\end{equation}
%where $V_n$ is the (complex) anisotropic flow coefficient in the $n$th harmonic.
%One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
This profile fluctuates event-by-event due to fluctuating position of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlation between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
%The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
The higher order harmonics are expected to be sensitive to fluctuations in the initial conditions and to the magnitude of $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while $v_{n}$ correlations have the potential to discriminate between these two respective contributions~\cite{Niemi:2012aj}.
%And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.

Difficulties in extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions in the models used for comparison~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
Viscous effects also reduce the magnitude of the elliptic flow. Furthermore, the magnitude of $\eta/s$ used in hydrodynamic calculations should be considered as an average over the temperature evolution of the expanding fireball as it is known that $\eta/s$ depends on temperature. 
In addition, part of the elliptic flow can also originate from the hadronic phase~\cite{Bozek:2011ua,Rose:2014fba,Ryu:2015vwa}. Therefore,
both the temperature dependence of $\eta/s$ and the relative contributions from the partonic and hadronic phases should be understood better to quantify the $\eta/s$ of the QGP.

An important input to the hydrodynamic model simulations is the initial distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricity~\cite{Alver:2010gr},
\begin{equation}
 \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
  \label{eq:eccentricities}
\end{equation}
where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g. $v_n \propto \varepsilon_n$ for $n$=2 or 3).
$v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
The higher harmonics ($n>3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}. When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to the ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
Hence, studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.

Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}. 
The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
In this article, we have extended the analysis of SC observables to higher order Fourier harmonics (up to $5^{\mathrm{th}}$ order) as well as measured the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also include extensive comparisons to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods. The experimental setup and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. The results of the measurements are presented in Sec.~\ref{sec:results}. 
 In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations. Various theoretical models used in this article are described in Sec.~\ref{sec:theory}. Sec.~\ref{sec:summary} summarizes our findings.

@@

Existing measurements provide an estimate of the average value of $\eta/s$ of the QGP, both at RHIC and LHC energies. What remains uncertain is how the $\eta/s$ of the QGP depends on temperature ($T$). The temperature dependence of $\eta/s$ in the QGP was discussed in ~\cite{Csernai:2006zz}. The effects on hadron spectra and elliptic flow were studied in ~\cite{Niemi:2011ix} for different parametrizations of $\eta/s(T)$.  A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations has just been initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein). The emerging picture is that the study of individual flow harmonics $v_n$ alone are unlikely to reveal the details of the temperature dependence of $\eta/s$.
It was already demonstrated in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics. In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$. These new observables have the potential to discriminate between the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}. Therefore their measurement would provide experimental constraints on theoretical predictions for the individual stages of heavy-ion system evolution independently. In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.

For reasons discussed in \cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced in \cite{Niemi:2012aj}. 
Based on \cite{Bilandzic:2013kga}, new flow observables obtained from multiparticle correlations, \textit{Symmetric Cumulants~(SC)}, were introduced. SC observables are nearly insensitive to nonflow and quantify the correlation of the amplitudes of two different flow harmonics.
The first measurements of SC observables were recently published by the ALICE Collaboration in \cite{ALICE:2016kpq}.

The SC observables are defined as:
 %
%\begin{widetext}
\begin{eqnarray}
\left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
&&{}-\left<\left<\cos[m(\varphi_1\!-\!\varphi_2)]\right>\right>\left<\left<\cos[n(\varphi_1\!-\!\varphi_2)]\right>\right>\nonumber\\
&=&\left<v_{m}^2v_{n}^2\right>-\left<v_{m}^2\right>\left<v_{n}^2\right>\,,%\nonumber\\
%&=&0\,.
\label{eq:4p_cumulant}
\end{eqnarray}
%\end{widetext}
%
with the condition $m\neq n$ for two positive integers $m$ and $n$ (for details see Sec.~IV~C in~\cite{Bilandzic:2013kga}).
In this article SC($m$,$n$) normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$~\cite{ALICE:2016kpq,Giacalone:2016afq} is denoted by NSC($m$,$n$):
%
\begin{equation}
\mathrm{NSC}(m,n) \equiv \frac{\mathrm{SC}(m,n)}{\left<v_{m}^2\right>\left<v_{n}^2\right>}\,.
\label{eq:nsc}
\end{equation}
%
Normalized symmetric cumulants reflect only the strength of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics. In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta|>1.0$ which suppresses biases from few-particle nonflow correlations. For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}) the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this case. This was verified by HIJING model simulations in \cite{ALICE:2016kpq}.

The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}. However, the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}. The observed centrality dependence of SC(4,2) cannot be captured by the models with constant $\eta/s$, indicating clearly that the temperature dependence of $\eta/s$ plays an important role. These results were also used to discriminate between different parameterizations of initial conditions. It was demonstrated that in the fluctuation-dominated regime (central collisions), MC-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.

\section{Data Analysis}
\label{sec:experiment}
Data recorded by ALICE in $\PbPb$ collisions at $\snn=2.76$~TeV during the 2010 heavy-ion run at the
LHC is used for this analysis. Detailed descriptions of the ALICE
detector can be found
in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
Projection Chamber (TPC) was used to reconstruct charged particle
tracks and measure their momenta with full azimuthal coverage in the
pseudorapidity range $|\eta|<0.8$. Two scintillator
arrays (V0) which cover the pseudo-rapidity ranges $-3.7<\eta<-1.7$
and $2.8<\eta<5.1$ were used for triggering and the determination of
centrality~\cite{Aamodt:2010cz}. The trigger
conditions and the event selection criteria are identical to those
described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
Approximately $10^7$ minimum-bias $\PbPb$ events with
a reconstructed primary vertex within $\pm 10$ cm from the nominal
interaction point along the beam direction are selected. Charged particles reconstructed in the TPC in $|\eta|<0.8$
and $0.2<p_{\rm T}<5$~GeV/$c$ were selected. The charged track quality cuts
described in~\cite{Aamodt:2010pa} were applied to minimize
contamination from secondary charged particles and fake tracks.
The track reconstruction efficiency and contamination
were estimated from HIJING Monte Carlo
simulations~\cite{Wang:1991hta} combined with a GEANT3~\cite{Brun:1994aa} detector model and were found to be independent of
the collision centrality. The reconstruction efficiency increases from
70\% to 80\% for particles with $0.2<p_{\rm T}<1$~GeV/$c$ and remains
constant at $(80 \pm 5)$\% for $p_{\rm T}>1$~GeV/$c$. The estimated
contamination by secondary charged particles from weak decays and
photon conversions is less than 6\% at $p_{\rm T}=0.2$~GeV/$c$ and falls
below 1\% for $p_{\rm T}>1$~GeV/$c$.
The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effect of jets on the measured correlations. 
Reconstructed TPC tracks were required to have at least 70 space points (out of a maximum of 159). 
Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted. This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc. Tracks with kinks (i.e, tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.

@@

The systematic uncertainties are estimated by varying the event and track selection criteria. All systematic checks described here are performed independently. 
The SC$(m,n)$ values resulting from each variation are compared to ones from the default event and track selection described in the previous section,
and differences are taken as the systematic uncertainty due to each individual source.
The contributions from different sources were added in quadrature to obtain the total systematic uncertainty.
